---
title: "Supplementary Software for Aquaculture is more regulated than any other food sector in the United States by Hegwood et al"
author: "Margaret Hegwood"
output: html_document
---
#load necessary libraries
```{r, warning = FALSE}
library(readxl)
library(tidyr)
library(dplyr)
library(ggplot2)
library(scales)
library(geomtextpath)
library(reshape2)
library(ggrepel)
library(patchwork)
library(gridExtra)
library(stringr)
library(ggpubr)
library(forcats)
```

#Create custom figure colors
```{r}
custom_colors <- c("Aquaculture" = "#0D98BA", "Crop Farming" = "#EC9706", "Fishing" = "#0000dc", "Hunting and Trapping" = "#004D40" , "Terrestrial Animal Farming" = "#A52A2A")
```

#MAIN TEXT FIGURES

#Figure 1: (A) Direct regulations over time for food industries (B) Direct regulations vs emissions intensity
```{r}
#Figure 1B
#Load Figure 1A data and Food Industries
fig1 <- inner_join(read_xlsx("Supplementary_Data_1.xlsx", "Figure 1A",  trim_ws = F),
                   read_xlsx("Supplementary_Data_1.xlsx", "Food Industries",  trim_ws = F), 
                   by = "industry_code")

fig1$date <- as.Date(fig1$date) #Make `date` in date format 
fig1$industry_code <- as.integer(fig1$industry_code) #make industry code integer format

#Sector Average data
average_data <- fig1 %>%
  group_by(date, sector) %>%
  dplyr::summarise(Average = mean(total_regulations)) %>%
  ungroup()

f1a <- fig1 %>%
  ggplot() + 
  geom_line(aes(x = date, y = total_regulations, group = industry_code, color = sector), alpha = 0.2) + 
  geom_line(data = average_data, aes(x = date, y = Average, color = sector), alpha = 1, size = 1) + 
  scale_color_manual(values = custom_colors) + 
  ylab("Direct Regulations") + 
  xlab("Year") +
  scale_x_date(date_labels = "%Y", breaks = seq(as.Date("1970-01-01"), max(fig1$date), by = '10 years')) +
  theme_bw() + 
  scale_y_continuous(labels = comma) +
  theme(legend.position = c(.05, .95),
        legend.justification = c("left", "top"),
        legend.box.just = "left",
        legend.margin = margin(1,1,1,1),
        legend.key.size = unit(1, 'cm'), #change legend key size
        legend.key.height = unit(0.25, 'cm'), #change legend key height
        legend.key.width = unit(0.25, 'cm'), #change legend key width
        legend.title = element_text(size=12, face = "bold"), #change legend title font size
        axis.text = element_text(size = 12), 
        axis.title = element_text(size = 18), 
        legend.text = element_text(size = 12)) + #change legend text font size
  labs(color = "Food Sector") + 
  geom_text_repel(data = fig1 %>% 
                     filter(date == "2010-01-01", industry_name == "Finfish Farming and Fish Hatcheries"), 
                   aes(x = date, y = total_regulations), 
                   label = c("Finfish Farming"), 
                   color = "#0D98BA", 
                   nudge_x = -3000, 
                   nudge_y = 750, 
                   size = 4) + 
   geom_text_repel(data = fig1 %>% 
                     filter(date == "2015-01-01", industry_name == "Shellfish Farming"), 
                   aes(x = date, y = total_regulations), 
                   label = c("Shellfish Farming"), 
                   color = "#0D98BA", 
                   nudge_x = -1500, 
                   nudge_y = 4000, 
                   size = 4) + 
    geom_text_repel(data = fig1 %>% 
                     filter(date == "2010-01-01", industry_name == "Other Aquaculture"), 
                   aes(x = date, y = total_regulations), 
                   label = c("Other Aquaculture"), 
                   color = "#0D98BA", 
                   nudge_x = 1000, 
                   nudge_y = -8500, 
                   size = 4) 
  
#Figure 1B
footprint <- read_xlsx("Supplementary_Data_1.xlsx", "Figure 1B and S3",  trim_ws = F)
footprint <- footprint %>%
  mutate(across(c(product,sector, industry_code), ~ str_replace_all(., " ", " ")))

#create average footprint by sector
avg_footprint <- footprint %>% group_by(sector) %>%
  summarize(avg = mean(ghg_median), 
            avg2 = mean(total_regulations)) 


f1b <- footprint %>% ggplot() + 
  geom_point(aes(x = ghg_median, y =total_regulations, shape = author, color= sector), alpha = 0.2, size =2) +
  geom_point(data = avg_footprint, aes(x=avg, y = avg2, color = sector), size = 4, shape = "diamond") +
  theme_bw() + 
  scale_shape_manual(values = c("circle", "square")) +
    scale_color_manual(values = custom_colors) +
  geom_text_repel(data = footprint %>% filter(product == "Bovine Meat (beef herd)"), aes(x = ghg_median, y = total_regulations), label = c("Beef"), color = "#A52A2A", nudge_x = -3, nudge_y = 10000) + 
  geom_text_repel(data = footprint %>% filter(product == "Bovine Meat (dairy herd)"), aes(x = ghg_median, y = total_regulations), label = c("Dairy Beef"), color = "#A52A2A", nudge_x = -3, nudge_y = 3000) +
   geom_text_repel(data = footprint %>% filter(product == "Milk"), aes(x = ghg_median, y = total_regulations), label = c("Milk"), color = "#A52A2A", nudge_x = 3, nudge_y = 3000)  +
     geom_text_repel(data = footprint %>% filter(product == "Lamb & Mutton"), aes(x = ghg_median, y = total_regulations), label = c("Lamb & Mutton"), color = "#A52A2A", nudge_x = -3, nudge_y = 8000) + 
     geom_text_repel(data = footprint %>% filter(product == "miscellaneous diadromous fishes (farmed)"), aes(x = ghg_median, y = total_regulations), label = c("Farmed Misc. Diadromous Fishes"), color = "#0D98BA", nudge_x = 3, nudge_y = 3000) + 
  geom_text_repel(data = footprint %>% filter(product == "seaweeds (farmed)"), aes(x = ghg_median, y = total_regulations), label = c("Farmed Seaweeds"), color = "#0D98BA", nudge_x = 3, nudge_y = -3000) + 
  geom_text_repel(data = footprint %>% filter(product == "flounders, halibuts, soles"), aes(x = ghg_median, y = total_regulations), label = c("Flounders, Halibuts, & Soles"), color = "#0000dc", nudge_x = 8, nudge_y = -3000) + 
  geom_text_repel(data = footprint %>% filter(product == "herrings, sardines, anchovies"), aes(x = ghg_median, y = total_regulations), label = c("Herrings, Sardines, & Anchovies"), color = "#0000dc", nudge_x = -8, 
             nudge_y = -6000) + 
  geom_text_repel(data = footprint %>% filter(product == "Olive Oil"), aes(x = ghg_median, y = total_regulations), label = c("Olive Oil"), color = "#EC9706", nudge_x = 5, nudge_y = 3000) + 
  geom_text_repel(data = footprint %>% filter(product == "Nuts"), aes(x = ghg_median, y = total_regulations), label = c("Nuts"), color = "#EC9706", nudge_x = -5, nudge_y = -3000) + 
  theme(legend.position = "none", 
        axis.text = element_text(size = 12), 
        axis.title = element_text(size = 18), 
        legend.text = element_text(size = 12), 
        plot.caption = element_text(hjust = 0)) +
  xlab(expression("Emissions (kg CO"[2]*"e/kg Product)")) + 
  ylab("Direct Regulations") + 
  ylim(c(-5000, 65000)) +
    scale_y_continuous(labels = comma) +
  labs(caption = str_wrap("Fig. 1 (A) Direct regulations from 1970 to 2020 for 44 food industries, with sector averages in bold. (B) Direct regula-tions in 2020 on food industries compared to their products GHG emissions intensities (squares (Poore & Nemecek, 2018), circles (Gephart et al, 2021)), with diamonds showing sector averages.", 120, whitespace_only = FALSE))


f1_final <- ggarrange(f1a, f1b,
          labels = c("A", "B"),
          ncol = 1, nrow = 2)

ggsave("Fig1_final_w_caption.pdf", f1_final,width = 8, height = 12, dpi = 300)

```

#Figure 1 Statistics
```{r}
#DESCRIPTIVE STATISTICS FIGURE 1A

#Difference in sector regulations in 2020
fig1_stat <- fig1 %>% filter(date == "2020-01-01")
fig1_stat <- fig1_stat %>% group_by(sector) %>%
  dplyr::summarise(avg_reg = mean(total_regulations), 
                   sd_reg = sd(total_regulations)) 

#Calculate difference from aquaculture
fig1_stat <- fig1_stat %>% mutate(aqua_diff = 58596.1971/avg_reg )

#Calculate difference from crops
fig1_stat <- fig1_stat %>% mutate(crop_diff = 20423.7515/avg_reg)


#TIME SERIES STATISTICS
#Average total direct regulations by sector per year 
fig1_stat_2 <-  fig1 %>%
  group_by(sector, date) %>% 
  dplyr::summarise(avg_reg = mean(total_regulations), 
                   sd_reg = sd(total_regulations)) 

#Annual percent change in regulations for each sector in each year
aqua_avg_regulations <- fig1_stat_2 %>% group_by(sector) %>%
  mutate(yoy = (log(avg_reg) - log(lag(avg_reg))) *100)  

#Year-to-Year (yoy) average percent change in regulations by secgtor over the time period 1970-2020
aqua_avg_regulations <- aqua_avg_regulations %>% group_by(sector) %>%
  dplyr::summarise(yoy_avg = mean(yoy, na.rm = TRUE), 
                   yoy_sd = sd(yoy, na.rm= TRUE)) 


```

#Figure 2: Total direct regulations by sector across federal agencies
```{r}
fig2 <-  inner_join(read_xlsx("Supplementary_Data_1.xlsx", "Figure 2 and S4",  trim_ws = F),
                   read_xlsx("Supplementary_Data_1.xlsx", "Food Industries",  trim_ws = F), 
                   by = "industry_code")

avg_agency <- fig2 %>% group_by(sector, agency) %>%
  summarize(avg = mean(total_regulations))

#calculate the top five agencies for each industry
top_group <- avg_agency %>% 
  group_by(sector) %>%
  slice_max(avg,n =6)

#Filter out all top unique regulating agencies
top_group <- unique(top_group$agency)


#Add line function
addline_format <- function(x,...){
    gsub('\\s','\n',x)
}


#example crops (maize, soy, vegetables)
f2 <- avg_agency %>%
  ggplot(aes(x = sector, y = avg, fill = agency)) + 
  geom_bar(stat = "identity", position = "stack") + 
  theme_bw() + 
  gghighlight::gghighlight(agency %in% top_group[c(1:10)], 
                           label_key = agency, 
                           use_group_by = FALSE,
                           use_direct_label = FALSE) + 
  scale_x_discrete(labels = addline_format(c("Aquaculture", "Crop Farming", "Fishing", "Hunting and Trapping", "Terrestrial Livestock Farming"))) + 
  scale_fill_manual(values= c("#034937", "#0a88d1", "#090088", 
                               "#064477", "#f4b655", "#7e3b26",
                               "#dcc962","#c10821", "#279640","#4f7b85")) +
  theme(legend.position = c(.95, .95),
        legend.justification = c("right", "top"),
        legend.box.just = "left",
        legend.margin = margin(1,1,1,1),
        legend.key.size = unit(1, 'cm'), #change legend key size
        legend.key.height = unit(0.25, 'cm'), #change legend key height
        legend.key.width = unit(0.25, 'cm'), #change legend key width
        legend.title = element_text(size=12, face = "bold"), #change legend title font size
        axis.text = element_text(size = 12), 
        axis.title = element_text(size = 18), 
        legend.text = element_text(size = 12), 
        plot.caption = element_text(hjust = 0)) + #change legend text font size
   xlab("Food Sector") + 
   ylab("2020 Direct Regulations") + 
   labs(fill = "Federal Government Agency") + 
   scale_y_continuous(labels = comma) +
   labs(caption = str_wrap("Fig. 2 Direct 2020 regulations from the top ten food industry regulating agencies are shown, with all other agencies aggregated in gray.", 200, whitespace_only = FALSE))
 
 
 ggsave("Fig2_final_caption.pdf", f2, width = 12, height = 6, dpi = 300) 
```


#SUPPLEMENTARY FIGURES

#Figure S1: Fraction of regulations from low probability documents
```{r}
figs1 <- inner_join(read_xlsx("Supplementary_Data_1.xlsx", "Figure S1",  trim_ws = F),
                   read_xlsx("Supplementary_Data_1.xlsx", "Food Industries",  trim_ws = F), 
                   by = "industry_code")
  
figs1$all_a <- as.character(figs1$all_a)
figs1 <- figs1 %>% pivot_longer(cols = starts_with("a"), names_to = "prob", values_to = "regs")
figs1$date = as.Date(figs1$date)
figs1$regs = as.numeric(figs1$regs)
figs1[is.na(figs1)] <- 0

average_data <- figs1 %>%
  group_by(date, sector, prob) %>%
  summarise(Average = mean(regs, na.rm = TRUE))

facet_labels <- c("all_a" = "All a", "a_0.10" = "a \u2265 0.1", "a_0.25" = "a \u2265 0.25", "a_0.5" = "a \u2265 0.5", "a_0.75" = "a \u2265 0.75", "a_0.9" = "a \u2265 0.9")

s1 <- figs1 %>% ggplot() + 
  geom_line(aes(x = date, y = regs, color = sector, group = industry_code), alpha = 0.2) + 
  geom_line(data = average_data %>% filter(prob != "total7"), aes(x = date, y = Average, color = sector), alpha = 1) +
  scale_x_date(date_labels = "%Y", breaks = seq(as.Date("1970-01-01"), max(figs1$date), by = '10 years')) +
  scale_color_manual(values = custom_colors) +
  theme_bw() +
  facet_wrap(~prob, nrow = 3, ncol = 2, labeller = as_labeller(facet_labels)) + 
   theme(legend.position = c(.025, 0.975),
        legend.justification = c("left", "top"),
        legend.box.just = "left",
        legend.margin = margin(1,1,1,1),
        legend.key.size = unit(0.01, 'cm'), #change legend key size
        legend.key.height = unit(0.25, 'cm'), #change legend key height
        legend.key.width = unit(0.25, 'cm'), #change legend key width
        legend.title = element_text(size=12, face = "bold"), #change legend title font size
        axis.text = element_text(size = 12), 
        axis.title = element_text(size =18), 
        legend.text = element_text(size = 12), 
        strip.text = element_text(size = 16),
        plot.caption = element_text(hjust = 0)) + #change legend text font size
  labs(color = "Food Sector") +
    scale_y_continuous(labels = comma) +
  xlab("Year") + 
  ylab("Direct Regulations") +
  labs(caption = str_wrap("Direct regulations with different probability cutoffs. Here, we replicate the results from Figure 1a of our main text using different a_pyi values. The title of each figure represents the cutoff. For example, a ≥ 0.25 means that regulations from all documents with a probability greater than or equal to 0.25 were summed to calculate the direct regulations for each six-digit NAICS food industry. As the cutoff increases towards 1 (i.e., 100% probability) we observed an overall decrease in regulations for each industry, but consistent trends across industries.", 160, whitespace_only = FALSE))

ggsave("FigS1_final_w_caption.png", s1, width = 10, height = 12, dpi = 300) 
```

#Figure S2: Total Regulations (Direct + Indirect) 
```{r}
#Load Supply-Utilization Spreadsheet from the Bureau of Economic Affairs (BEA)
bea_2017 <- read_xlsx("Supplementary_Data_1.xlsx", "BEA USE Table",  trim_ws = F)

colnames(bea_2017) <- bea_2017[5,] #rename columns correctly using values in row 4
bea_2017 <- bea_2017[-c(1:5),-2] #delete rows 1 through 4, as well as column 2
bea_2017 <- mutate_at(bea_2017, vars(-matches("Code")), as.numeric) 

#filter out construction data and make one large construction category (Any codes that start with 23)
construction <- bea_2017 %>%
  filter(grepl("^23", Code)) %>%
  summarise(across(-c(Code), sum)) 
names1 <- colnames(construction)
construction <- construction %>% mutate(Code = 23)
construction <- construction[, c("Code", names1)]

#filter our real estate data and make one large real estate category (Codes = 531HST, 531ORE)
realEstate <- bea_2017 %>%
  filter(grepl("^531", Code)) %>%
  summarise(across(-c(Code), sum))
names2 <- colnames(realEstate)
realEstate <- realEstate %>% mutate(Code = 531)
realEstate <- realEstate[, c("Code", names2)]

#remove original construction data from I-O data
bea_2017 <- bea_2017 %>% filter(!grepl("^23", Code), !grepl("^531", Code))

#add summarized row of construction data back to io weights
bea_2017  <- rbind(bea_2017, construction)
bea_2017  <- rbind(bea_2017, realEstate)

#Adjust construction (23) and real estate (531) columns
bea_2017 <- bea_2017 %>% mutate(`23` = rowSums(select(.,starts_with("23"))))
bea_2017 <- bea_2017 %>% mutate(`531` = rowSums(select(.,starts_with("531"))))

bea_2017 <- bea_2017 %>% pivot_longer(cols = -c(`Code`), names_to = "Code2", values_to = "contribute")

#CONVERT BEA CODES TO NAICS 2017 codes
bea_to_naics <- read_xlsx("Supplementary_Data_1.xlsx", "BEA to NAICS Crosswalk",  trim_ws = F)
bea_to_naics <- separate_rows(bea_to_naics, `industry_code_2017`, sep = ", ") 
bea_to_naics <- bea_to_naics %>% filter(`industry_code_2017` != "NA")

#Replace NAICS 2017 codes with NAICS 2007 codes to match with RegData
bea_2017_to_2007 <- read_xlsx("Supplementary_Data_1.xlsx", "NAICS Crosswalk",  trim_ws = F)
bea_2017_to_2007$industry_code_2017 <- as.character(bea_2017_to_2007$industry_code_2017)
bea_to_naics <- full_join(bea_to_naics, bea_2017_to_2007, by = "industry_code_2017", relationship = "many-to-many")
colnames(bea_to_naics)[1] <- c("Code")

#Merge BEA 2017 with NAICS codes to transfer Code1
bea_2017_naics <- inner_join(bea_to_naics, bea_2017, by = "Code", relationship = "many-to-many") #results in many-to-many warning, this is expected

#Remove unnecessary descriptor columns
bea_2017_naics <- bea_2017_naics[,c("industry_code", "contribute", "Code2")]

#Rename columns to convert Code2 
colnames(bea_2017_naics) <- c("NAICS1", "contribute", "Code")

#Merge BEA 2017 with NAICS codes a second time to transfer Code2 (renamed Code in the line above to do the join)
bea_2017_naics <- inner_join(bea_2017_naics, bea_to_naics[, c("industry_code", "Code")], by = "Code", relationship = "many-to-many")

#Delete old BEA columns
bea_2017_naics <- bea_2017_naics[,c("NAICS1", "industry_code", "contribute")]

#Rename columns
colnames(bea_2017_naics) <- c("NAICS1", "NAICS2", "contribute")

#Split contribution equally amongst NAICS codes
test <- bea_2017_naics 

test2 <- as.data.frame(table(test$NAICS1, test$contribute))
colnames(test2) <-  c("NAICS1", "contribute", "freq")
test$NAICS1 <- as.factor(test$NAICS1)
test$contribute <- as.factor(test$contribute)

test <- full_join(test, test2, by = c("NAICS1", "contribute"))

test <- test %>% mutate(final_contribute = as.numeric(contribute)/freq)

bea_2017_naics <- test[, c("NAICS1", "NAICS2", "final_contribute")] 

colnames(bea_2017_naics) <- c("NAICS1", "NAICS2", "contribute")                                       
                                       

#Create a function that replaces any value >0 with 1
replace_greater_than_0 <- function(x) {
  ifelse(x > 0, 1, x)
}

#Create a new column that preserves the original values of the contribute column
bea_2017_naics <- bea_2017_naics %>% mutate(contribute2 = contribute)

cols_to_modify <- colnames(bea_2017_naics[,c(3)])

bea_2017_naics[cols_to_modify] <- sapply(bea_2017_naics[,cols_to_modify], replace_greater_than_0) #turn all numeric values to 1 when >0

#Merge direct and indirect regulations
indirect_regulations <- bea_2017_naics 

colnames(indirect_regulations) <- c("industry_code", "NAICS2", "contribute", "contribute2")

indirect_regulations <- indirect_regulations  %>% filter(substr(NAICS2, 1,2) == 11) #we only need indirect regulations for the food industry

temp <- read_xlsx("Supplementary_Data_1.xlsx", "Figure 1A",  trim_ws = F)
temp$industry_code <- as.factor(temp$industry_code)

indirect_regulations <- inner_join(indirect_regulations, temp, by = "industry_code")

colnames(indirect_regulations) <- c("industry_indirect", "industry_code", "contribute", "contribute2", "date", "total")

#Additive Regulations Approach
indirect_regulations <- indirect_regulations %>% mutate(indirect_regulations = total*contribute)

#Multiplicative Regulations Approach (Staples et al 2022)
indirect_regulations <- indirect_regulations %>% 
  group_by(industry_code, date) %>%
  mutate(indirect_regulations2 = total*contribute*contribute2/sum(contribute2, na.rm = TRUE))

#Sum all indirect regulations for each year
indirect_regulations2 <- indirect_regulations %>% 
  group_by(date, industry_code) %>% 
  mutate(total_indirect1 = sum(indirect_regulations, na.rm = TRUE), 
         total_indirect2 = sum(indirect_regulations2, na.rm = TRUE))

indirect_regulations2 <- indirect_regulations2[,c("industry_code", "date", "total_indirect1", "total_indirect2")]
indirect_regulations2 <- unique(indirect_regulations2)
indirect_regulations2$industry_code <- as.integer(indirect_regulations2$industry_code)


indirect_regulations3 <- inner_join(indirect_regulations2, fig1, by = c("industry_code", "date"))


indirect_regulations3 <- indirect_regulations3 %>% mutate(total_overall1 = total_regulations + total_indirect1, 
                                                          total_overall2 = total_regulations + total_indirect2)

indirect_regulations3$date <- as.Date(indirect_regulations3$date) 
#Average data
average_data <- indirect_regulations3 %>%
  group_by(date, sector) %>%
  summarise(average1 = mean(total_overall1, na.rm = TRUE), 
           average2 = mean(total_overall2, na.rm = TRUE))

average_data$date <- as.Date(average_data$date)

s2 <- indirect_regulations3 %>%
  ggplot() + 
  geom_line(aes(x = date, y = total_overall1, group = industry_name, color = sector), alpha = 0.2, size = 0.5) + 
  geom_line(data = average_data , aes(x = date, y = jitter(average1), color = sector), alpha = 1, size = 0.5) + 
  scale_color_manual(values = custom_colors) + 
  ylab("Total Regulations (Direct + Indirect)") + 
  xlab("Year") +
  scale_x_date(date_labels = "%Y", breaks = seq(as.Date("1970-01-01"), max(fig1$date), by = '10 years')) +
  theme_bw() + 
  scale_y_continuous(labels = comma) +
  theme(legend.position = "none",
        axis.text = element_text(size = 12), 
        axis.title = element_text(size = 18), 
        legend.text = element_text(size = 12), 
        plot.caption =  element_text(hjust = 0)) + #change legend text font size
  labs(color = "Food Sector") +
  labs(caption = str_wrap("Total regulations over time, including direct and indirect regulations. (A) Represents the multiplicative approach, where indirect regulations are weighted based on their fractional contribution to gross domestic product (GDP). (B) Represents the additive approach where regulations from every input industry are added together. Note that with this approach Hunting and Trapping and Fishing have a very similar number of total regulations, which result in near overlapping lines.", 120, whitespace_only = FALSE))

        
  
#Add position = position_jitter(width = 0, height = 50000)#fig1Add position = position_jitter(width = 0, height = 50000)

s3 <- indirect_regulations3 %>%
  ggplot() + 
  geom_line(aes(x = date, y = total_overall2, group = industry_name, color = sector), alpha = 0.2, size = 0.5) + 
  geom_line(data = average_data , aes(x = date, y = jitter(average2), color = sector), alpha = 1, size = 0.5) + 
  scale_color_manual(values = custom_colors) + 
  ylab("Total Regulations (Direct + Indirect)") + 
  xlab("Year") +
  scale_x_date(date_labels = "%Y", breaks = seq(as.Date("1970-01-01"), max(fig1$date), by = '10 years')) +
  theme_bw() + 
  scale_y_continuous(labels = comma) +
  theme(legend.position = c(.05, .95),
        legend.justification = c("left", "top"),
        legend.box.just = "left",
        legend.margin = margin(1,1,1,1),
        legend.key.size = unit(1, 'cm'), #change legend key size
        legend.key.height = unit(0.25, 'cm'), #change legend key height
        legend.key.width = unit(0.25, 'cm'), #change legend key width
        legend.title = element_text(size=12, face = "bold"), #change legend title font size
        axis.text = element_text(size = 12), 
        axis.title = element_text(size = 18), 
        legend.text = element_text(size = 12)) + #change legend text font size
  labs(color = "Food Sector") 

s2_final <- ggarrange(s3, s2 + rremove("ylab"), 
          labels = c("A", "B"),
          ncol = 1, nrow = 2)

ggsave("FigS2_final_w_caption.pdf", s2_final, width = 8, height = 12, dpi = 300) 


```

#Figure S3: Environmental Footprint vs Regulations
```{r}

#Direct regs vs. environmental footprint w/ error bars
S4a <-  footprint %>% ggplot() + 
  geom_point(aes(x = ghg_median, y =total_regulations, shape = author, color = sector), alpha = 0.2, size =4) +
  geom_errorbarh(aes(xmin=ghg_5, xmax=ghg_95, y = total_regulations, color = sector, height = 2000), alpha = 0.2)  +
  theme_bw() + 
  scale_shape_manual(values = c("circle", "square")) +
    scale_color_manual(values = custom_colors) +
 theme(legend.position = "none",
        axis.text = element_text(size = 12), 
        axis.title = element_text(size = 18), 
        legend.text = element_text(size = 12)) +
  xlab(expression("Emissions (kg CO"[2]*"e/kg Product)")) + 
  ylab("Direct Regulations") + 
    scale_y_continuous(labels = comma) 

S4b <-  footprint %>% ggplot() + 
  geom_point(aes(x = ghg_median, y =env_regulations, shape = author, color = sector), alpha = 0.2, size =4) +
  geom_errorbarh(aes(xmin=ghg_5, xmax=ghg_95, y = env_regulations, color = sector, height = 500), alpha = 0.2) +
  theme_bw() + 
  scale_shape_manual(values = c("circle", "square")) +
    scale_color_manual(values = custom_colors) +
 theme(legend.position = c(0.6, .95),
        legend.justification = c("left", "top"),
        legend.box.just = "left",
        legend.margin = margin(1,1,1,1),
        legend.key.size = unit(1, 'cm'), #change legend key size
        legend.key.height = unit(0.25, 'cm'), #change legend key height
        legend.key.width = unit(0.25, 'cm'), #change legend key width
        legend.title = element_text(size=12, face = "bold"), #change legend title font size
        axis.text = element_text(size = 12), 
        axis.title = element_text(size = 18), 
        legend.text = element_text(size = 12)) +
  xlab(expression("Emissions (kg CO"[2]*"e/kg Product)")) + 
  ylab("Direct Environmental Regulations") + 
    scale_y_continuous(labels = comma) 

S4c <-  footprint %>% ggplot() + 
  geom_point(aes(x = ghg_median, y =total_overall1, shape = author, color = sector), alpha = 0.2, size =4) +
  geom_errorbarh(aes(xmin=ghg_5, xmax=ghg_95, y = total_overall1, color = sector, height = 10^5), alpha = 0.2) +
  theme_bw() + 
  scale_shape_manual(values = c("circle", "square")) +
    scale_color_manual(values = custom_colors) +
  theme(legend.position = "none", 
        axis.text = element_text(size = 12), 
        axis.title = element_text(size = 18), 
        legend.text = element_text(size = 12)) +
  xlab(expression("Emissions (kg CO"[2]*"e/kg Product)")) + 
  ylab("Total Regulations (Direct + Indirect)") + 
    scale_y_continuous(labels = comma) 

S4d <-  footprint %>% ggplot() + 
  geom_point(aes(x = ghg_median, y =total_overall2, shape = author, color = sector), alpha = 0.2, size =4) +
  geom_errorbarh(aes(xmin=ghg_5, xmax=ghg_95, y = total_overall2, color = sector, height = 1000), alpha = 0.2) +
  theme_bw() + 
  scale_shape_manual(values = c("circle", "square")) +
    scale_color_manual(values = custom_colors) +
  theme(legend.position = "none", 
        axis.text = element_text(size = 12), 
        axis.title = element_text(size = 18), 
        legend.text = element_text(size = 12)) +
  xlab(expression("Emissions (kg CO"[2]*"e/kg Product)")) + 
  ylab("Total Regulations (Direct + Indirect)") + 
    scale_y_continuous(labels = comma) 

s4_final <- ggarrange(S4a, S4b, S4c, S4d,
          labels = c("A", "B", "C", "D"),
          ncol = 2, nrow = 2)


ggsave("FigS3_final.png", s4_final,width = 16, height = 12, dpi = 300)
```

#Figure S4: Direct Regulations by Federal Agency for Food Industries
```{r}

figs4 <- fig2 %>% filter(substr(industry_code, 1,2) == 11)

figs4 <- figs4 %>% group_by(industry_code) %>%
  mutate(pt_reg = total_regulations/sum(total_regulations, na.rm = TRUE)*100)

s1 <- figs4 %>% filter(pt_reg > 1) %>%
  ggplot(aes(x = as.factor(industry_code), y = agency, fill = sector))+
  geom_tile(aes(alpha = pt_reg), color = "white") + 
  theme_bw() +
  scale_fill_manual(values = custom_colors, na.value = 'white') +
  scale_alpha_continuous(range = c(0,1)) +
  scale_y_discrete(limits=rev) + # labels = label_wrap(40)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1),
        legend.position = "bottom",
        legend.justification = c("center", "top"),
        legend.margin = margin(1,1,1,1),
        legend.key.size = unit(1, 'cm'), #change legend key size
        legend.key.height = unit(2, 'cm'), #change legend key height
        legend.key.width = unit(2, 'cm'), #change legend key width
        legend.title = element_text(size=40, face = "bold"), #change legend title font size
        axis.text = element_text(size = 30), 
        axis.title = element_text(size = 45), 
        legend.text = element_text(size = 45), #change legend text font size
        legend.box = "vertical") +  
  xlab("Industry (2007 NAICS Code)") + 
  ylab("Federal Government Agency") + 
  labs(fill = "Food Sector", alpha = "Percent of Total Direct Regulations") +
  coord_equal()


 ggsave("FigS4_final.png", s1, width = 50, height = 40, dpi = 300, limitsize = FALSE) 
```

#Figure S5: Direct regulations by CFR Title for Food Industries
```{r}
figs5 <- inner_join(read_xlsx("Supplementary_Data_1.xlsx", "Figure S5",  trim_ws = F),
                   read_xlsx("Supplementary_Data_1.xlsx", "Food Industries",  trim_ws = F), 
                   by = "industry_code")

figs5  <- figs5 %>% mutate(title_whole = paste0("Title ", title_number, ": ", title_description))

figs5  <- figs5 %>% group_by(industry_code) %>%
  mutate(pt_reg = total_regulations / sum(total_regulations, na.rm = TRUE)*100)

figs5  <- figs5[order(figs5$title_number),]

s1 <- figs5 %>% 
  mutate(title_whole = fct_reorder(title_whole, title_number)) %>%
  ggplot(aes(x = as.factor(industry_code), y = title_whole, fill = sector)) + 
  geom_tile(aes(alpha = pt_reg), color = "white") + 
  theme_bw() +
  scale_fill_manual(values = custom_colors, na.value = 'white') +
  scale_alpha_continuous(range = c(0,1)) +
  scale_y_discrete(limits=rev) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1),
        legend.position = "bottom",
        legend.justification = c("center", "top"),
        legend.margin = margin(1,1,1,1),
        legend.key.size = unit(1, 'cm'), #change legend key size
        legend.key.height = unit(2, 'cm'), #change legend key height
        legend.key.width = unit(2, 'cm'), #change legend key width
        legend.title = element_text(size=30, face = "bold"), #change legend title font size
        axis.text = element_text(size =30), 
        axis.title = element_text(size = 40), 
        legend.text = element_text(size = 40), #change legend text font size
        legend.box = "vertical") +  #change legend text font size
  xlab("Industry (2007 NAICS Code)") + 
  ylab("Code of Federal Regulations Title") + 
  labs(fill = "Food Sector", alpha = "Percent of Total Direct Regulations") +
  coord_equal()


 ggsave("FigS5_final.png", s1, width = 40, height = 30, dpi = 300) 
```
