---
title: "Supplementary Software for Aquaculture is subject to more regulations than any other food sector in the United States by Hegwood et al"
author: "Margaret Hegwood et al"
output: html_document
---
#load necessary libraries
```{r, include= FALSE}
library(readxl)
library(tidyr)
library(dplyr)
library(ggplot2)
library(scales)
library(geomtextpath)
library(reshape2)
library(ggrepel)
library(patchwork)
library(gridExtra)
library(stringr)
library(ggpubr)
library(forcats)
library(gghighlight)
library(gtable)
library(lemon)
library(grid)
```

#Create custom figure colors
```{r}
custom_colors <- c("Aquaculture" = "#0D98BA", "Crop Farming" = "#EC9706", "Fishing" = "#0000dc", "Hunting and Trapping" = "#004D40" , "Terrestrial Animal Farming" = "#A52A2A")
```

#Generate addline function
```{r}
#Add line function
addline_format <- function(x,...){
    gsub('\\s','\n',x)
}
```

#MAIN TEXT FIGURES

#Figure 1
```{r}
#Load Figure 1A source data and Food Industries
fig1 <- merge(read_xlsx("Supplementary_Dataset_1.xlsx", "Figure 1",  trim_ws = F), 
              read_xlsx("Supplementary_Dataset_1.xlsx", "Food Industries",  trim_ws = F), 
                   by = c("industry_code"))
                  
#transform date into date format
fig1$date <- as.Date(fig1$date) #Make `date` in date format 

#make industry code integer format
fig1$industry_code <- as.integer(fig1$industry_code) 

#Calculate change percent change in regulations per year
fig1 <- fig1 %>% mutate(yoy = (total_regulations- lag(total_regulations))/lag(total_regulations*100))


#Calculate sector Average data
average_data <- fig1 %>%
  group_by(date, sector) %>%
  dplyr::summarise(Average = mean(total_regulations), 
                   Average_yoy = mean(yoy)) %>%
  ungroup()


#Create Figure 1
p1 <- fig1 %>%
  ggplot() + 
  geom_line(aes(x = date, y = total_regulations, group = industry_code, color = sector), alpha = 0.2) + 
  geom_line(data = average_data, aes(x = date, y = Average, color = sector), alpha = 1, linewidth = 1) + 
  scale_color_manual(values = custom_colors) + 
  ylab("Direct Regulations") + 
  xlab("Year") +
  scale_x_date(date_labels = "%Y", breaks = seq(as.Date("1970-01-01"), max(fig1$date), by = '10 years')) +
  theme_bw() + 
  scale_y_continuous(labels = comma) +
  theme(legend.position = c(.05, .95),
        legend.justification = c("left", "top"),
        legend.box.just = "left",
        legend.margin = margin(1,1,1,1),
        legend.key.size = unit(1, 'cm'), #change legend key size
        legend.key.height = unit(0.25, 'cm'), #change legend key height
        legend.key.width = unit(0.25, 'cm'), #change legend key width
        legend.title = element_text(size=12, face = "bold"), #change legend title font size
        axis.text = element_text(size = 12), 
        axis.title = element_text(size = 18), 
        legend.text = element_text(size = 12)) + #change legend text font size
  labs(color = "Food Sector") + 
  geom_text_repel(data = fig1 %>% 
                     filter(date == "2010-01-01", industry_name == "Finfish Farming and Fish Hatcheries"), 
                   aes(x = date, y = total_regulations), 
                   label = c("Finfish Farming"), 
                   color = "#0D98BA", 
                   nudge_x = -3000, 
                   nudge_y = 750, 
                   size = 4) + 
   geom_text_repel(data = fig1 %>% 
                     filter(date == "2015-01-01", industry_name == "Shellfish Farming"), 
                   aes(x = date, y = total_regulations), 
                   label = c("Shellfish Farming"), 
                   color = "#0D98BA", 
                   nudge_x = -1500, 
                   nudge_y = 4000, 
                   size = 4) + 
    geom_text_repel(data = fig1 %>% 
                     filter(date == "2010-01-01", industry_name == "Other Aquaculture"), 
                   aes(x = date, y = total_regulations), 
                   label = c("Other Aquaculture"), 
                   color = "#0D98BA", 
                   nudge_x = 1000, 
                   nudge_y = -8500, 
                   size = 4) + 
  geom_text_repel(data = fig1 %>% 
                     filter(date == "2010-01-01", industry_name == "Other Vegetable (except Potato) and Melon Farming"), 
                   aes(x = date, y = total_regulations), 
                   label = c("Other Vegetable and Melon Farming"), 
                   color = "#EC9706", 
                   nudge_x = -2000, 
                   nudge_y = 4000, 
                   size = 4) +
    geom_text_repel(data = fig1 %>% 
                     filter(date == "2010-01-01", industry_name == "Hog and Pig Farming"), 
                   aes(x = date, y = total_regulations), 
                   label = c("Hog and Pig Farming"), 
                   color = "#A52A2A", 
                   nudge_x = -2000, 
                   nudge_y = 2000, 
                   size = 4) +
  geom_vline(aes(xintercept = as.Date("1991-01-01")), color = "darkgrey", linetype = "dashed", size = 1) + 
   geom_text_repel(data = fig1 %>% 
                     filter(date == "1991-01-01", industry_name == "Sugar Beet Farming"), 
                   aes(x = date, y = 30000), 
                   label = addline_format("1991-Aquaculture regulations surpass all other industries"), 
                   color = "darkgrey", 
                   nudge_x = -2500, 
                   nudge_y = 10000, 
                   size = 4)  

ggsave("Fig1.png", p1, width = 8.5, height = 7, dpi = 300)

```

#Figure 1 Statistics
```{r}
#DESCRIPTIVE STATISTICS FIGURE 1A

#Difference in sector regulations in 2020
fig1_stat <- fig1 %>% filter(date == "2020-01-01")
fig1_stat <- fig1_stat %>% group_by(sector) %>%
  dplyr::summarise(avg_reg = mean(total_regulations), 
                   sd_reg = sd(total_regulations)) 

#Calculate difference from aquaculture in 2020
fig1_stat <- fig1_stat %>% mutate(aqua_diff = 58596.1971/avg_reg )

#Calculate difference from crops in 2020
fig1_stat <- fig1_stat %>% mutate(crop_diff = 20423.7515/avg_reg)


#TIME SERIES STATISTICS
#Average total direct regulations by sector per year 
fig1_stat_2 <-  fig1 %>%
  group_by(sector, date) %>% 
  dplyr::summarise(avg_reg = mean(total_regulations), 
                   sd_reg = sd(total_regulations)) 

#Annual percent change in regulations for each sector in each year
aqua_avg_regulations <- fig1_stat_2 %>% group_by(sector) %>%
  mutate(yoy = (log(avg_reg) - log(lag(avg_reg))) *100)  

#Year-to-Year (yoy) average percent change in regulations by secgtor over the time period 1970-2020
aqua_avg_regulations <- aqua_avg_regulations %>% group_by(sector) %>%
  dplyr::summarise(yoy_avg = mean(yoy, na.rm = TRUE), 
                   yoy_sd = sd(yoy, na.rm= TRUE)) 


```

#Figure 2
```{r}
#Load data for Figure 2A
p2a <- inner_join(read_xlsx("Supplementary_Dataset_1.xlsx", "Figure 2A",  trim_ws = F),
                   read_xlsx("Supplementary_Dataset_1.xlsx", "Food Industries",  trim_ws = F), 
                   by = "industry_code")

p2a <- p2a %>% mutate(title_whole = paste0("Title ", title_number, ": ", title_description))

p2a  <- p2a %>% group_by(industry_code) %>%
  mutate(pt_reg = total_regulations / sum(total_regulations, na.rm = TRUE)*100)

p2a <- p2a %>% group_by(sector, title_number, title_whole) %>%
  summarise(pt_reg = mean(pt_reg), 
            total= mean(total_regulations))

p2a$title_whole <- fct_reorder(p2a$title_whole, p2a$title_number)

xlabels <- unique(p2a$title_whole)

fig2a <- p2a %>% 
  #mutate(title_whole = fct_reorder(title_whole, title_number)) %>%
  ggplot(aes(x = as.factor(sector), y = title_whole, fill = sector)) + 
  geom_tile(aes(alpha = pt_reg), color = "white") + 
  theme_bw() +
  scale_fill_manual(values = custom_colors, na.value = 'white') +
  scale_alpha_continuous(range = c(0,1)) +
  scale_y_discrete(limits=rev, 
                   labels = function(x) str_trunc(rev(as.character(xlabels)), width = 20)) +
  theme(axis.text.x = element_blank(),
        legend.position = "bottom",
        legend.justification = c("center", "top"),
        legend.margin = margin(.2,.2,.2,.2),
        legend.key.size = unit(.2, 'cm'), #change legend key size
        legend.key.height = unit(.2, 'cm'), #change legend key height
        legend.key.width = unit(.2, 'cm'), #change legend key width
        legend.title = element_text(size=12, face = "bold"), #change legend title font size
        axis.text = element_text(size =12), 
        axis.title = element_text(size = 18), 
        legend.text = element_text(size = 12), #change legend text font size
        legend.box = "vertical", 
        axis.text.y = element_text(hjust = 0)) +  #change legend text font size
  xlab("Sector") + 
  ylab("Code of Federal Regulations Title") + 
  labs(fill = "Food Sector", alpha = "% total") +
  coord_equal()

p2b <- inner_join(read_xlsx("Supplementary_Dataset_1.xlsx", "Figure 2B", trim_ws = F), 
                        read_xlsx("Supplementary_Dataset_1.xlsx", "Food Industries",  trim_ws = F), 
                        by = c("industry_code"))

p2b$date <- as.Date(p2b$date)

#reorder data by relevant titles
p2b$title <-  factor(p2b$title , levels=c("Title 7", "Title 9", "Title 21", "Title 33", "Title 40", "Title 50"), labels = c("Title 7: Agriculture", 
                                            "Title 9: Animals and Animal Products", 
                                            "Title 21: Food and Drugs", 
                                            "Title 33: Navigation and Navigable Waters", 
                                            "Title 40: Protection of Environment", 
                                            "Title 50: Wildlife and Fisheries"))

avg_title <- p2b %>% group_by(title, date, sector) %>%
  dplyr::summarise(total = mean(total_regulations))

avg_title$date <- as.Date(avg_title$date)

fig2b <- p2b %>%
  ggplot() + 
  geom_line(aes(x = date, y = total_regulations, group = industry_code, color = sector), alpha = 0.2) + 
  geom_line(data = avg_title, aes(x = date, y = total, color = sector), alpha = 1, size = 1) +
   facet_wrap(~title, nrow = 3, ncol = 2) +
   scale_color_manual(values = custom_colors) + 
  ylab("Direct Regulations") + 
  xlab("Year") +
  scale_x_date(date_labels = "%Y", breaks = seq(as.Date("1970-01-01"), max(p2b$date), by = '10 years')) +
  theme_bw() + 
  scale_y_continuous(labels = comma) +
  theme(legend.position = c(.05, .95),
        legend.justification = c("left", "top"),
        legend.box.just = "left",
        legend.margin = margin(1,1,1,1),
        legend.key.size = unit(1, 'cm'), #change legend key size
        legend.key.height = unit(0.25, 'cm'), #change legend key height
        legend.key.width = unit(0.25, 'cm'), #change legend key width
        legend.title = element_text(size=16, face = "bold"), #change legend title font size
        axis.text = element_text(size = 12), 
        axis.title = element_text(size = 18), 
        legend.text = element_text(size = 16), 
        strip.text = element_text(size = 12), 
        strip.background = element_rect(fill = "white")) + #change legend text font size
  labs(color = "Food Sector") 
 
fig2 <- ggarrange(fig2a,fig2b, 
                  labels = c("A", "B"), 
                  widths = c(0.5,1),
                  common.legend = TRUE, 
                  legend= "bottom")


ggsave("Fig2_final.png", fig2,width = 11, height = 9, dpi = 300)
```

#Figure 3
```{r}
p3 <-  inner_join(read_xlsx("Supplementary_Dataset_1.xlsx", "Figure 3",  trim_ws = F),
                   read_xlsx("Supplementary_Dataset_1.xlsx", "Food Industries",  trim_ws = F), 
                   by = "industry_code")

avg_agency <- p3 %>% group_by(sector, agency) %>%
  summarize(avg = mean(total_regulations))

#calculate the top five agencies for each industry
top_group <- avg_agency %>% 
  group_by(sector) %>%
  slice_max(avg,n =6)

#Filter out all top unique regulating agencies
top_group <- unique(top_group$agency)


#Add line function
addline_format <- function(x,...){
    gsub('\\s','\n',x)
}


#example crops (maize, soy, vegetables)
fig3 <- avg_agency %>%
  ggplot(aes(x = sector, y = avg, fill = agency)) + 
  geom_bar(stat = "identity", position = "stack") + 
  theme_bw() + 
  gghighlight::gghighlight(agency %in% top_group[c(1:10)], 
                           label_key = agency, 
                           use_group_by = FALSE,
                           use_direct_label = FALSE) + 
  scale_x_discrete(labels = addline_format(c("Aquaculture", "Crop Farming", "Fishing", "Hunting and Trapping", "Terrestrial Animal Farming"))) + 
  scale_fill_manual(values= c("#034937", "#0a88d1", "#090088", 
                               "#064477", "#f4b655", "#7e3b26",
                               "#dcc962","#c10821", "#279640","#4f7b85")) +
  theme(legend.position = c(.95, .95),
        legend.justification = c("right", "top"),
        legend.box.just = "left",
        legend.margin = margin(1,1,1,1),
        legend.key.size = unit(1, 'cm'), #change legend key size
        legend.key.height = unit(0.25, 'cm'), #change legend key height
        legend.key.width = unit(0.25, 'cm'), #change legend key width
        legend.title = element_text(size=12, face = "bold"), #change legend title font size
        axis.text = element_text(size = 12), 
        axis.title = element_text(size = 18), 
        legend.text = element_text(size = 12), 
        plot.caption = element_text(hjust = 0)) + #change legend text font size
   xlab("Food Sector") + 
   ylab("Direct Regulations") + 
   labs(fill = "Federal Government Agency") + 
   scale_y_continuous(labels = comma) 

ggsave("Fig3_final.png", fig3,width = 8, height = 4, dpi = 300)
``` 
 
#Figure 4
```{r}
#Figure 4
footprint <- read_xlsx("Supplementary_Dataset_1.xlsx", "Figure 4 and S3",  trim_ws = F)
footprint <- footprint %>%
  mutate(across(c(product,sector, industry_code), ~ str_replace_all(., " ", " ")))

#create average footprint by sector
avg_footprint <- footprint %>% group_by(sector) %>%
  summarize(avg_reg = mean(total_regulations),
            avg_env = mean(env_regulations),
            avg_ghg = mean(ghg_median), 
            avg_land = mean(land_median), 
            avg_freshwater = mean(freshwater_median)) 


f4a <- footprint %>% ggplot() + 
  geom_point(aes(x = ghg_median, y =total_regulations, shape = author, color= sector), alpha = 0.2, size =4) +
  geom_point(data = avg_footprint, aes(x=avg_ghg, y = avg_reg, color = sector), size = 6, shape = "diamond") +
  theme_bw() + 
  scale_shape_manual(values = c("circle", "square")) +
    scale_color_manual(values = custom_colors) +
  geom_text_repel(data = footprint %>% filter(product == "Bovine Meat (beef herd)"), aes(x = ghg_median, y = total_regulations), label = c("Beef"), color = "#A52A2A", nudge_x = -3, nudge_y = 10000, size = 5) + 
  geom_text_repel(data = footprint %>% filter(product == "Bovine Meat (dairy herd)"), aes(x = ghg_median, y = total_regulations), label = c("Dairy Beef"), color = "#A52A2A", nudge_x = -3, nudge_y = 5000, size = 5) +
   geom_text_repel(data = footprint %>% filter(product == "Milk"), aes(x = ghg_median, y = total_regulations), label = c("Milk"), color = "#A52A2A", nudge_x = 3, nudge_y = 5000, size = 5)  +
     geom_text_repel(data = footprint %>% filter(product == "Lamb & Mutton"), aes(x = ghg_median, y = total_regulations), label = c("Lamb & Mutton"), color = "#A52A2A", nudge_x = -2, nudge_y = 8000, size = 5) + 
     geom_text_repel(data = footprint %>% filter(product == "miscellaneous diadromous fishes (farmed)"), aes(x = ghg_median, y = total_regulations), label = c("Farmed Misc. Diadromous Fishes"), color = "#0D98BA", nudge_x = 3, nudge_y = 4000, size = 5) + 
  geom_text_repel(data = footprint %>% filter(product == "seaweeds (farmed)"), aes(x = ghg_median, y = total_regulations), label = c("Farmed Seaweeds"), color = "#0D98BA", nudge_x = 3, nudge_y = -4000, size = 5) + 
  geom_text_repel(data = footprint %>% filter(product == "flounders, halibuts, soles"), aes(x = ghg_median, y = total_regulations), label = c("Flounders, Halibuts, & Soles"), color = "#0000dc", nudge_x = 8, nudge_y = -6000, size = 5) + 
  geom_text_repel(data = footprint %>% filter(product == "herrings, sardines, anchovies"), aes(x = ghg_median, y = total_regulations), label = c("Herrings, Sardines, & Anchovies"), color = "#0000dc", nudge_x = 8, nudge_y = -10000, size = 5) + 
  geom_text_repel(data = footprint %>% filter(product == "Olive Oil"), aes(x = ghg_median, y = total_regulations), label = c("Olive Oil"), color = "#EC9706", nudge_x = 5, nudge_y = 4000, size = 5) + 
  geom_text_repel(data = footprint %>% filter(product == "Nuts"), aes(x = ghg_median, y = total_regulations), label = c("Nuts"), color = "#EC9706", nudge_x = 3, nudge_y = 6000, size = 5) + 
  theme(legend.position = "none", 
        axis.text = element_text(size = 12), 
        axis.title = element_text(size = 18), 
        legend.text = element_text(size = 12), 
        plot.caption = element_text(hjust = 0), 
        axis.title.x=element_blank()) +
  #xlab(expression("Emissions (kg CO"[2]*"e/kg product)")) + 
  ylab("Direct Regulations") + 
  ylim(c(-5000, 65000)) +
    scale_y_continuous(labels = comma) + 
    labs(color = "Food Sector")+ 
  guides(shape = "none")

f4b <- footprint %>% filter(sector != "Fishing") %>% ggplot() + 
  geom_point(aes(x = land_median, y =total_regulations, shape = author, color= sector), alpha = 0.2, size =4) +
  geom_point(data = avg_footprint, aes(x=avg_land, y = avg_reg, color = sector), size = 6, shape = "diamond") +
  theme_bw() + 
  scale_shape_manual(values = c("circle", "square")) +
    scale_color_manual(values = custom_colors) +
  geom_text_repel(data = footprint %>% filter(product == "Bovine Meat (beef herd)"), aes(x = land_median, y = total_regulations), label = c("Beef"), color = "#A52A2A", nudge_x = -3, nudge_y = 10000, size = 5) + 
  geom_text_repel(data = footprint %>% filter(product == "Milk"), aes(x = land_median, y = total_regulations), label = c("Milk"), color = "#A52A2A", nudge_x = 6, nudge_y = 6000, size = 5) +
     geom_text_repel(data = footprint %>% filter(product == "Lamb & Mutton"), aes(x = land_median, y = total_regulations), label = c("Lamb & Mutton"), color = "#A52A2A", nudge_x = -3, nudge_y = 8000, size = 5) +
     geom_text_repel(data = footprint %>% filter(product == "milkfish (farmed)"), aes(x = land_median, y = total_regulations), label = c("Farmed Milkfish"), color = "#0D98BA", nudge_x = 3, nudge_y = 10000, size = 5) + 
  geom_text_repel(data = footprint %>% filter(product == "seaweeds (farmed)"), aes(x = land_median, y = total_regulations), label = c("Farmed Seaweeds"), color = "#0D98BA", nudge_x = 3, nudge_y = -10000, size = 5) + 
    geom_text_repel(data = footprint %>% filter(product == "Olive Oil"), aes(x = land_median, y = total_regulations), label = c("Olive Oil"), color = "#EC9706", nudge_x = 5, nudge_y = 6000, size = 5) + 
  geom_text_repel(data = footprint %>% filter(product == "Tomatoes"), aes(x = land_median, y = total_regulations), label = c("Tomatoes"), color = "#EC9706", nudge_x = 5, nudge_y = 6000, size = 5) + 
  theme(legend.position = "none", 
        axis.text = element_text(size = 12), 
        axis.title = element_text(size = 18), 
        legend.text = element_text(size = 12), 
        plot.caption = element_text(hjust = 0),
        axis.title.x=element_blank(), 
        axis.title.y=element_blank()) +
  #xlab(expression("Land Use (m"^2*"/FU)")) + 
  #ylab("Direct Regulations") + 
  ylim(c(-5000, 65000)) +
    scale_y_continuous(labels = comma)+ 
    labs(color = "Food Sector")+ 
  guides(shape = "none")

f4c <- footprint %>% filter(sector != "Fishing") %>% ggplot() + 
  geom_point(aes(x = freshwater_median, y =total_regulations, shape = author, color= sector), alpha = 0.2, size =4) +
  geom_point(data = avg_footprint, aes(x=avg_freshwater, y = avg_reg, color = sector), size = 6, shape = "diamond") +
  theme_bw() + 
  scale_shape_manual(values = c("circle", "square")) +
    scale_color_manual(values = custom_colors) +
   geom_text_repel(data = footprint %>% filter(product == "Pig Meat"), aes(x = freshwater_median, y = total_regulations), label = c("Pig Meat"), color = "#A52A2A", nudge_x = 3, nudge_y = 5000, size = 5) + 
  geom_text_repel(data = footprint %>% filter(product == "Bovine Meat (dairy herd)"), aes(x = freshwater_median, y = total_regulations), label = c("Dairy Beef"), color = "#A52A2A", nudge_x = 750, nudge_y = 4000, size = 5) +
  geom_text_repel(data = footprint %>% filter(product == "Milk"), aes(x = freshwater_median, y = total_regulations), label = c("Milk"), color = "#A52A2A", nudge_x = -3, nudge_y = 6000, size = 5) +
    geom_text_repel(data = footprint %>% filter(product == "Nuts"), aes(x = freshwater_median, y = total_regulations), label = c("Nuts"), color = "#EC9706", nudge_x = 500, nudge_y = 5000, size = 5) + 
  geom_text_repel(data = footprint %>% filter(product == "Rice"), aes(x = freshwater_median, y = total_regulations), label = c("Rice"), color = "#EC9706", nudge_x = 750, nudge_y = 8500, size = 5) + 
    geom_text_repel(data = footprint %>% filter(product == "Cassava"), aes(x = freshwater_median, y = total_regulations), label = c("Cassava"), color = "#EC9706", nudge_x = 5, nudge_y = 5000, size = 5) + 
  geom_text_repel(data = footprint %>% filter(product == "silver or bighead carp (farmed)"), aes(x = freshwater_median, y = total_regulations), label = c("Farmed Silver or Bighead Carp"), color = "#0D98BA", nudge_x = 3, nudge_y = 10000, size = 5) + 
  geom_text_repel(data = footprint %>% filter(product == "other carps, barbels and cyprinids (farmed)"), aes(x = freshwater_median, y = total_regulations), label = c("Farmed Other Carps, Barbels and Cyprinids"), color = "#0D98BA", nudge_x = 5, nudge_y = -14000, size = 5) + 
  geom_text_repel(data = footprint %>% filter(product == "seaweeds (farmed)"), aes(x = freshwater_median, y = total_regulations), label = c("Farmed Seaweeds"), color = "#0D98BA", nudge_x = 3, nudge_y = -4000, size = 5) +
  theme(legend.position = "none", 
        axis.text = element_text(size = 12), 
        axis.title = element_text(size = 18), 
        legend.text = element_text(size = 12), 
        plot.caption = element_text(hjust = 0),
          axis.title.x=element_blank(), 
        axis.title.y=element_blank()) +
  #xlab(expression("Water Use (L/FU)")) + 
  #ylab("Direct Regulations") + 
  ylim(c(-5000, 65000)) +
    scale_y_continuous(labels = comma) + 
    labs(color = "Food Sector")+ 
  guides(shape = "none")

f4d <- footprint %>% ggplot() + 
  geom_point(aes(x = ghg_median, y =env_regulations, shape = author, color= sector), alpha = 0.2, size =4) +
  geom_point(data = avg_footprint, aes(x=avg_ghg, y = avg_env, color = sector), size = 6, shape = "diamond") +
  theme_bw() + 
  scale_shape_manual(values = c("circle", "square")) +
    scale_color_manual(values = custom_colors) +
  geom_text_repel(data = footprint %>% filter(product == "Bovine Meat (beef herd)"), aes(x = ghg_median, y = env_regulations), label = c("Beef"), color = "#A52A2A", nudge_x = -3, nudge_y = 4000, size = 5) + 
  geom_text_repel(data = footprint %>% filter(product == "Bovine Meat (dairy herd)"), aes(x = ghg_median, y = env_regulations), label = c("Dairy Beef"), color = "#A52A2A", nudge_x = -4, nudge_y = 1000, size = 5) +
   geom_text_repel(data = footprint %>% filter(product == "Milk"), aes(x = ghg_median, y = env_regulations), label = c("Milk"), color = "#A52A2A", nudge_x = 3, nudge_y = 3000, size = 5)  +
     geom_text_repel(data = footprint %>% filter(product == "Lamb & Mutton"), aes(x = ghg_median, y = env_regulations), label = c("Lamb & Mutton"), color = "#A52A2A", nudge_x = -3, nudge_y = 2000, size = 5) + 
     geom_text_repel(data = footprint %>% filter(product == "miscellaneous diadromous fishes (farmed)"), aes(x = ghg_median, y = env_regulations), label = c("Farmed Misc. Diadromous Fishes"), color = "#0D98BA", nudge_x = 3, nudge_y = 3000, size = 5) + 
  geom_text_repel(data = footprint %>% filter(product == "seaweeds (farmed)"), aes(x = ghg_median, y = env_regulations), label = c("Farmed Seaweeds"), color = "#0D98BA", nudge_x = 3, nudge_y = -3000, size = 5) + 
  geom_text_repel(data = footprint %>% filter(product == "flounders, halibuts, soles"), aes(x = ghg_median, y = env_regulations), label = c("Flounders, Halibuts, & Soles"), color = "#0000dc", nudge_x = 8, nudge_y = -1000,size = 5) + 
  geom_text_repel(data = footprint %>% filter(product == "herrings, sardines, anchovies"), aes(x = ghg_median, y = env_regulations), label = c("Herrings, Sardines, & Anchovies"), color = "#0000dc", nudge_x = 16, nudge_y = -2000, size = 5) + 
  geom_text_repel(data = footprint %>% filter(product == "Olive Oil"), aes(x = ghg_median, y = env_regulations), label = c("Olive Oil"), color = "#EC9706", nudge_x = 5, nudge_y = 2000, size = 5) + 
  geom_text_repel(data = footprint %>% filter(product == "Nuts"), aes(x = ghg_median, y = env_regulations), label = c("Nuts"), color = "#EC9706", nudge_x = 0, nudge_y = 2000, size = 5) + 
  theme(legend.position = "none", 
        axis.text = element_text(size = 12), 
        axis.title = element_text(size = 18), 
        legend.text = element_text(size = 12), 
        plot.caption = element_text(hjust = 0)) +
  xlab(expression("Emissions (kg CO"[2]*"e/kg product)")) + 
  ylab("Direct Environmental Regulations") + 
  ylim(c(-5000, 65000)) +
    scale_y_continuous(labels = comma) + 
    labs(color = "Food Sector")+ 
  guides(shape = "none")


f4e <- footprint %>% filter(sector != "Fishing") %>% ggplot() + 
  geom_point(aes(x = land_median, y =env_regulations, shape = author, color= sector), alpha = 0.2, size =4) +
  geom_point(data = avg_footprint, aes(x=avg_land, y = avg_env, color = sector), size = 6, shape = "diamond") +
  theme_bw() + 
  scale_shape_manual(values = c("circle", "square")) +
    scale_color_manual(values = custom_colors) +
  geom_text_repel(data = footprint %>% filter(product == "Bovine Meat (beef herd)"), aes(x = land_median, y = env_regulations), label = c("Beef"), color = "#A52A2A", nudge_x = -3, nudge_y = 2000, size = 5) + 
  geom_text_repel(data = footprint %>% filter(product == "Milk"), aes(x = land_median, y = env_regulations), label = c("Milk"), color = "#A52A2A", nudge_x = 10, nudge_y = -2000, size = 5) +
     geom_text_repel(data = footprint %>% filter(product == "Lamb & Mutton"), aes(x = land_median, y = env_regulations), label = c("Lamb & Mutton"), color = "#A52A2A", nudge_x = -3, nudge_y = 3000, size = 5) +
     geom_text_repel(data = footprint %>% filter(product == "milkfish (farmed)"), aes(x = land_median, y = env_regulations), label = c("Farmed Milkfish"), color = "#0D98BA", nudge_x = 3, nudge_y = 2000, size = 5) + 
  geom_text_repel(data = footprint %>% filter(product == "seaweeds (farmed)"), aes(x = land_median, y = env_regulations), label = c("Farmed Seaweeds"), color = "#0D98BA", nudge_x = 3, nudge_y = -2000, size = 5) + 
    geom_text_repel(data = footprint %>% filter(product == "Olive Oil"), aes(x = land_median, y = env_regulations), label = c("Olive Oil"), color = "#EC9706", nudge_x = 5, nudge_y = 3000, size = 5) + 
  geom_text_repel(data = footprint %>% filter(product == "Tomatoes"), aes(x = land_median, y = env_regulations), label = c("Tomatoes"), color = "#EC9706", nudge_x = 5, nudge_y = 3000, size = 5) + 
  theme(legend.position = "none", 
        axis.text = element_text(size = 12), 
        axis.title = element_text(size = 18), 
        legend.text = element_text(size = 12), 
        plot.caption = element_text(hjust = 0),
        axis.title.y=element_blank()) +
  xlab(expression("Land Use (m"^2*"/kg product)")) + 
  #ylab("Environmental Regulations") + 
  ylim(c(-5000, 65000)) +
    scale_y_continuous(labels = comma) + 
    labs(color = "Food Sector")+ 
  guides(shape = "none")

f4f <- footprint %>% filter(sector != "Fishing") %>% ggplot() + 
  geom_point(aes(x = freshwater_median, y =env_regulations, shape = author, color= sector), alpha = 0.2, size =4) +
  geom_point(data = avg_footprint, aes(x=avg_freshwater, y = avg_env, color = sector), size = 6, shape = "diamond") +
  theme_bw() + 
  scale_shape_manual(values = c("circle", "square")) +
    scale_color_manual(values = custom_colors) +
   geom_text_repel(data = footprint %>% filter(product == "Pig Meat"), aes(x = freshwater_median, y = env_regulations), label = c("Pig Meat"), color = "#A52A2A", nudge_x = 750, nudge_y = -2000, size = 5) + 
  geom_text_repel(data = footprint %>% filter(product == "Bovine Meat (dairy herd)"), aes(x = freshwater_median, y = env_regulations), label = c("Dairy Beef"), color = "#A52A2A", nudge_x = 750, nudge_y = 1000, size = 5) +
  geom_text_repel(data = footprint %>% filter(product == "Milk"), aes(x = freshwater_median, y = env_regulations), label = c("Milk"), color = "#A52A2A", nudge_x = 750, nudge_y = 1000, size = 5) +
    geom_text_repel(data = footprint %>% filter(product == "Nuts"), aes(x = freshwater_median, y = env_regulations), label = c("Nuts"), color = "#EC9706", nudge_x = -500, nudge_y = -1000, size = 5) + 
  geom_text_repel(data = footprint %>% filter(product == "Rice"), aes(x = freshwater_median, y = env_regulations), label = c("Rice"), color = "#EC9706", nudge_x = 500, nudge_y = 2000, size = 5) + 
    geom_text_repel(data = footprint %>% filter(product == "Cassava"), aes(x = freshwater_median, y = env_regulations), label = c("Cassava"), color = "#EC9706", nudge_x = 5, nudge_y = 2000, size = 5) + 
  geom_text_repel(data = footprint %>% filter(product == "silver or bighead carp (farmed)"), aes(x = freshwater_median, y = env_regulations), label = c("Farmed Silver or Bighead Carp"), color = "#0D98BA", nudge_x = 3, nudge_y = 1000, size = 5) + 
  geom_text_repel(data = footprint %>% filter(product == "other carps, barbels and cyprinids (farmed)"), aes(x = freshwater_median, y = env_regulations), label = c("Farmed Other Carps, Barbels and Cyprinids"), color = "#0D98BA", nudge_x = 5, nudge_y = -2000, size = 5) + 
  geom_text_repel(data = footprint %>% filter(product == "seaweeds (farmed)"), aes(x = freshwater_median, y = env_regulations), label = c("Farmed Seaweeds"), color = "#0D98BA", nudge_x = 3, nudge_y = -800, size = 5) +
  theme(legend.position = "bottom", 
        axis.text = element_text(size = 12), 
        axis.title = element_text(size = 18), 
        legend.text = element_text(size = 12), 
        plot.caption = element_text(hjust = 0),
        axis.title.y=element_blank()) +
  xlab(expression("Freshwater withdrawals (L/kg product)")) + 
  #ylab("Environmental Regulations") + 
  ylim(c(-5000, 65000)) +
    scale_y_continuous(labels = comma) + 
  labs(color = "Food Sector")+ 
  guides(shape = "none")


f4_final <- ggarrange(f4a,f4b,f4c,f4d,f4e, f4f,
          labels = c("A","B", "C", "D", "E", "F"),
          ncol = 3, nrow = 2, 
          align = "hv", 
          common.legend = TRUE, 
          legend = "bottom")

ggsave("Fig4_final.png", f4_final,width = 16, height = 10, dpi = 300)
```

#Figure 5: Cost-adjusted regulations
```{r}
cost <- read_xlsx("Supplementary_Dataset_1.xlsx", "Figure 5",  trim_ws = F)
#remove total columns
cost <- cost %>% filter(sector != "NA")
cost <- cost[,c("sector", "species", "adj_total_regulations")]

cost$adj_total_regulations <- as.numeric(cost$adj_total_regulations)
addline_format <- function(x,...){
    gsub('\\s','\n',x)
}

fig5<- cost %>% filter(sector == "Aquaculture") %>% 
  ggplot(aes(x=species, y = adj_total_regulations,fill = sector, group = species)) + geom_col() +
  scale_fill_manual(values = custom_colors) +
   geom_hline(data = cost %>% filter(sector != "Aquaculture"), aes(yintercept = adj_total_regulations, color = sector), linetype = "dashed") + 
  geom_text(
    data = cost %>% filter(sector != "Aquaculture"),
    aes(x =12.5,
        y = adj_total_regulations,
        label = sector,
        color = sector), hjust = 1, vjust = -.5, size = 4.5) +
  scale_color_manual(values = custom_colors) + 
  theme_bw() + 
  theme(axis.text = element_text(size = 12), 
        axis.title = element_text(size = 18), 
        legend.text = element_text(size = 12))+
  xlab("Aquaculture species") + 
  ylab("2020 cost-adjusted direct regulations") + 
  guides(fill = "none", color = "none")+
  scale_y_continuous(labels = comma) +
   scale_x_discrete(labels = function(x) str_wrap(x, width = 10))



ggsave("Fig5.png", fig5, width = 12, height = 5, dpi = 300)

```


#SUPPLEMENTARY FIGURES

#Figure S1: Fraction of regulations from low probability documents
```{r}
figs1 <- inner_join(read_xlsx("Supplementary_Dataset_1.xlsx", "Figure S1",  trim_ws = F),
                   read_xlsx("Supplementary_Dataset_1.xlsx", "Food Industries",  trim_ws = F), 
                   by = "industry_code")
  
figs1$all_a <- as.character(figs1$all_a)
figs1 <- figs1 %>% pivot_longer(cols = starts_with("a"), names_to = "prob", values_to = "regs")
figs1$date = as.Date(figs1$date)
figs1$regs = as.numeric(figs1$regs)
figs1[is.na(figs1)] <- 0

average_data <- figs1 %>%
  group_by(date, sector, prob) %>%
  summarise(Average = mean(regs, na.rm = TRUE))

facet_labels <- c("all_a" = "All a", "a_0.10" = "a \u2265 0.1", "a_0.25" = "a \u2265 0.25", "a_0.5" = "a \u2265 0.5", "a_0.75" = "a \u2265 0.75", "a_0.9" = "a \u2265 0.9")

s1 <- figs1 %>% ggplot() + 
  geom_line(aes(x = date, y = regs, color = sector, group = industry_code), alpha = 0.2) + 
  geom_line(data = average_data %>% filter(prob != "total7"), aes(x = date, y = Average, color = sector), alpha = 1) +
  scale_x_date(date_labels = "%Y", breaks = seq(as.Date("1970-01-01"), max(figs1$date), by = '10 years')) +
  scale_color_manual(values = custom_colors) +
  theme_bw() +
  facet_wrap(~prob, nrow = 3, ncol = 2, labeller = as_labeller(facet_labels)) + 
   theme(legend.position = c(.025, 0.975),
        legend.justification = c("left", "top"),
        legend.box.just = "left",
        legend.margin = margin(1,1,1,1),
        legend.key.size = unit(0.01, 'cm'), #change legend key size
        legend.key.height = unit(0.25, 'cm'), #change legend key height
        legend.key.width = unit(0.25, 'cm'), #change legend key width
        legend.title = element_text(size=12, face = "bold"), #change legend title font size
        axis.text = element_text(size = 12), 
        axis.title = element_text(size =18), 
        legend.text = element_text(size = 12), 
        strip.text = element_text(size = 16),
        plot.caption = element_text(hjust = 0)) + #change legend text font size
  labs(color = "Food Sector") +
    scale_y_continuous(labels = comma) +
  xlab("Year") + 
  ylab("Direct Regulations")

ggsave("FigS1_final.png", s1, width = 10, height = 12, dpi = 300) 
```

#Figure S2: Total Regulations (Direct + Indirect) 
```{r, include = FALSE}
#Load Supply-Utilization Spreadsheet from the Bureau of Economic Affairs (BEA)
bea_2017 <- read_xlsx("Supplementary_Dataset_1.xlsx", "BEA USE Table",  trim_ws = F)

colnames(bea_2017) <- bea_2017[5,] #rename columns correctly using values in row 4
bea_2017 <- bea_2017[-c(1:5),-2] #delete rows 1 through 4, as well as column 2
bea_2017 <- mutate_at(bea_2017, vars(-matches("Code")), as.numeric) 

#filter out construction data and make one large construction category (Any codes that start with 23)
construction <- bea_2017 %>%
  filter(grepl("^23", Code)) %>%
  summarise(across(-c(Code), sum)) 
names1 <- colnames(construction)
construction <- construction %>% mutate(Code = 23)
construction <- construction[, c("Code", names1)]

#filter our real estate data and make one large real estate category (Codes = 531HST, 531ORE)
realEstate <- bea_2017 %>%
  filter(grepl("^531", Code)) %>%
  summarise(across(-c(Code), sum))
names2 <- colnames(realEstate)
realEstate <- realEstate %>% mutate(Code = 531)
realEstate <- realEstate[, c("Code", names2)]

#remove original construction data from I-O data
bea_2017 <- bea_2017 %>% filter(!grepl("^23", Code), !grepl("^531", Code))

#add summarized row of construction data back to io weights
bea_2017  <- rbind(bea_2017, construction)
bea_2017  <- rbind(bea_2017, realEstate)

#Adjust construction (23) and real estate (531) columns
bea_2017 <- bea_2017 %>% mutate(`23` = rowSums(select(.,starts_with("23"))))
bea_2017 <- bea_2017 %>% mutate(`531` = rowSums(select(.,starts_with("531"))))

bea_2017 <- bea_2017 %>% pivot_longer(cols = -c(`Code`), names_to = "Code2", values_to = "contribute")

#CONVERT BEA CODES TO NAICS 2017 codes
bea_to_naics <- read_xlsx("Supplementary_Dataset_1.xlsx", "BEA to NAICS Crosswalk",  trim_ws = F)
bea_to_naics <- separate_rows(bea_to_naics, `industry_code_2017`, sep = ", ") 
bea_to_naics <- bea_to_naics %>% filter(`industry_code_2017` != "NA")

#Replace NAICS 2017 codes with NAICS 2007 codes to match with RegData
bea_2017_to_2007 <- read_xlsx("Supplementary_Dataset_1.xlsx", "NAICS Crosswalk",  trim_ws = F)
bea_2017_to_2007$industry_code_2017 <- as.character(bea_2017_to_2007$industry_code_2017)
bea_to_naics <- full_join(bea_to_naics, bea_2017_to_2007, by = "industry_code_2017", relationship = "many-to-many")
colnames(bea_to_naics)[1] <- c("Code")

#Merge BEA 2017 with NAICS codes to transfer Code1
bea_2017_naics <- inner_join(bea_to_naics, bea_2017, by = "Code", relationship = "many-to-many") #results in many-to-many warning, this is expected

#Remove unnecessary descriptor columns
bea_2017_naics <- bea_2017_naics[,c("industry_code", "contribute", "Code2")]

#Rename columns to convert Code2 
colnames(bea_2017_naics) <- c("NAICS1", "contribute", "Code")

#Merge BEA 2017 with NAICS codes a second time to transfer Code2 (renamed Code in the line above to do the join)
bea_2017_naics <- inner_join(bea_2017_naics, bea_to_naics[, c("industry_code", "Code")], by = "Code", relationship = "many-to-many")

#Delete old BEA columns
bea_2017_naics <- bea_2017_naics[,c("NAICS1", "industry_code", "contribute")]

#Rename columns
colnames(bea_2017_naics) <- c("NAICS1", "NAICS2", "contribute")

#Split contribution equally amongst NAICS codes
test <- bea_2017_naics 

test2 <- as.data.frame(table(test$NAICS1, test$contribute))
colnames(test2) <-  c("NAICS1", "contribute", "freq")
test$NAICS1 <- as.factor(test$NAICS1)
test$contribute <- as.factor(test$contribute)

test <- full_join(test, test2, by = c("NAICS1", "contribute"))

test <- test %>% mutate(final_contribute = as.numeric(contribute)/freq)

bea_2017_naics <- test[, c("NAICS1", "NAICS2", "final_contribute")] 

colnames(bea_2017_naics) <- c("NAICS1", "NAICS2", "contribute")                                       
                                       

#Create a function that replaces any value >0 with 1
replace_greater_than_0 <- function(x) {
  ifelse(x > 0, 1, x)
}

#Create a new column that preserves the original values of the contribute column
bea_2017_naics <- bea_2017_naics %>% mutate(contribute2 = contribute)

cols_to_modify <- colnames(bea_2017_naics[,c(3)])

bea_2017_naics[cols_to_modify] <- sapply(bea_2017_naics[,cols_to_modify], replace_greater_than_0) #turn all numeric values to 1 when >0

#Merge direct and indirect regulations
indirect_regulations <- bea_2017_naics 

colnames(indirect_regulations) <- c("industry_code", "NAICS2", "contribute", "contribute2")

indirect_regulations <- indirect_regulations  %>% filter(substr(NAICS2, 1,2) == 11) #we only need indirect regulations for the food industry

temp <- read_xlsx("Supplementary_Dataset_1.xlsx", "Figure 1",  trim_ws = F)
temp$industry_code <- as.factor(temp$industry_code)

indirect_regulations <- inner_join(indirect_regulations, temp, by = "industry_code")

colnames(indirect_regulations) <- c("industry_indirect", "industry_code", "contribute", "contribute2", "date", "total")

#Additive Regulations Approach
indirect_regulations <- indirect_regulations %>% mutate(indirect_regulations = total*contribute)

#Multiplicative Regulations Approach (Staples et al 2022)
indirect_regulations <- indirect_regulations %>% 
  group_by(industry_code, date) %>%
  mutate(indirect_regulations2 = total*contribute*contribute2/sum(contribute2, na.rm = TRUE))

#Sum all indirect regulations for each year
indirect_regulations2 <- indirect_regulations %>% 
  group_by(date, industry_code) %>% 
  mutate(total_indirect1 = sum(indirect_regulations, na.rm = TRUE), 
         total_indirect2 = sum(indirect_regulations2, na.rm = TRUE))

indirect_regulations2 <- indirect_regulations2[,c("industry_code", "date", "total_indirect1", "total_indirect2")]
indirect_regulations2 <- unique(indirect_regulations2)
indirect_regulations2$industry_code <- as.integer(indirect_regulations2$industry_code)


indirect_regulations3 <- inner_join(indirect_regulations2, fig1, by = c("industry_code", "date"))


indirect_regulations3 <- indirect_regulations3 %>% mutate(total_overall1 = total_regulations + total_indirect1, 
                                                          total_overall2 = total_regulations + total_indirect2)

indirect_regulations3$date <- as.Date(indirect_regulations3$date) 
#Average data
average_data <- indirect_regulations3 %>%
  group_by(date, sector) %>%
  summarise(average1 = mean(total_overall1, na.rm = TRUE), 
           average2 = mean(total_overall2, na.rm = TRUE))

average_data$date <- as.Date(average_data$date)

s2 <- indirect_regulations3 %>%
  ggplot() + 
  geom_line(aes(x = date, y = total_overall1, group = industry_name, color = sector), alpha = 0.2, size = 0.5) + 
  geom_line(data = average_data , aes(x = date, y = jitter(average1), color = sector), alpha = 1, size = 0.5) + 
  scale_color_manual(values = custom_colors) + 
  ylab("Total Regulations (Direct + Indirect)") + 
  xlab("Year") +
  scale_x_date(date_labels = "%Y", breaks = seq(as.Date("1970-01-01"), max(fig1$date), by = '10 years')) +
  theme_bw() + 
  scale_y_continuous(labels = comma) +
  theme(legend.position = "none",
        axis.text = element_text(size = 12), 
        axis.title = element_text(size = 18), 
        legend.text = element_text(size = 12), 
        plot.caption =  element_text(hjust = 0)) + #change legend text font size
  labs(color = "Food Sector") 

        
  
#Add position = position_jitter(width = 0, height = 50000)#fig1Add position = position_jitter(width = 0, height = 50000)

s3 <- indirect_regulations3 %>%
  ggplot() + 
  geom_line(aes(x = date, y = total_overall2, group = industry_name, color = sector), alpha = 0.2, size = 0.5) + 
  geom_line(data = average_data , aes(x = date, y = jitter(average2), color = sector), alpha = 1, size = 0.5) + 
  scale_color_manual(values = custom_colors) + 
  ylab("Total Regulations (Direct + Indirect)") + 
  xlab("Year") +
  scale_x_date(date_labels = "%Y", breaks = seq(as.Date("1970-01-01"), max(fig1$date), by = '10 years')) +
  theme_bw() + 
  scale_y_continuous(labels = comma) +
  theme(legend.position = c(.05, .95),
        legend.justification = c("left", "top"),
        legend.box.just = "left",
        legend.margin = margin(1,1,1,1),
        legend.key.size = unit(1, 'cm'), #change legend key size
        legend.key.height = unit(0.25, 'cm'), #change legend key height
        legend.key.width = unit(0.25, 'cm'), #change legend key width
        legend.title = element_text(size=12, face = "bold"), #change legend title font size
        axis.text = element_text(size = 12), 
        axis.title = element_text(size = 18), 
        legend.text = element_text(size = 12)) + #change legend text font size
  labs(color = "Food Sector") 

s2_final <- ggarrange(s3, s2 + rremove("ylab"), 
          labels = c("A", "B"),
          ncol = 2, nrow = 1)

ggsave("FigS2_final.png", s2_final, width = 12, height = 8, dpi = 300) 


```

#Figure S3: Environmental Footprint vs Regulations
```{r}
footprint2 <- footprint %>% mutate(across(.cols = c(1:3),.fns = factor))
  
footprint2 <- footprint2 %>% mutate_if(is.character,as.numeric) #will generate warning becauase of missing values for aquaculture for some environmental impacts

footprint2 <- footprint2 %>% pivot_longer(cols = c("ghg_median", "land_median", "acid_median", "eutro_median", "freshwater_median", "stresswater_median"), 
                                         names_to = "impact", 
                                         values_to = "median")

footprint2 <- footprint2 %>% pivot_longer(cols = c("ghg_5", "land_5", "acid_5", "eutro_5", "freshwater_5", "stresswater_5"), 
                                          names_to = "impact_2", 
                                          values_to = "lower")

footprint2 <- footprint2 %>% mutate(impact = str_split(impact, "_", simplify = TRUE)[,1], 
                                    impact_2 = str_split(impact_2, "_", simplify = TRUE)[,1])

footprint2 <- footprint2 %>% filter(impact == impact_2)

footprint2 <- footprint2 %>% pivot_longer(cols = c("ghg_95", "land_95", "acid_95", "eutro_95", "freshwater_95", "stresswater_95"), 
                                          names_to = "impact_3", 
                                          values_to = "upper")

footprint2 <- footprint2 %>% mutate(impact_3 = str_split(impact_3, "_", simplify = TRUE)[,1])

footprint2 <- footprint2 %>% filter(impact == impact_2 & impact == impact_3)

facet_labels <- c("acid" = bquote('Number VS'~Number^2), 
                                            "eutro" = "B. Eutro. Pot. (kg PO4 eq)", 
                                            "freshwater" = "C. Freshwater use (L)", 
                                            "ghg" = "D. GHG Emissions (kg CO2 eq)", 
                                            "land" = "E. Land use (m^2)", 
                                            "stresswater" = "F. Scarc. weighted water use (L)")

footprint2 <- footprint2 %>% 
  mutate(impact = factor(impact, labels = c(bquote("a. Acid. emissions"~"(kg SO"[2]~"eq)"),
                                            bquote("b. Eutro. emissions"~"(kg PO"[4]^3-~"eq)"),
                                            bquote("c."~"Freshwater withdrawals"~"(L)"),
                                            bquote("d. GHG emissions"~"(kg CO"[2]~"eq)"), 
                                            bquote("e. Land use (m"^2~")"), 
                                            bquote("f. Stress-weighted water use"~"(L)"))))


figs3a <- footprint2 %>%
    ggplot() + 
  geom_point(aes(x = median, y = total_regulations, shape = author, color = sector), alpha = 0.2, size =3) +
  geom_errorbarh(aes(xmin=lower, xmax=upper, y = total_regulations, color = sector, height = 2000), alpha = 0.2)  +
  facet_wrap(~impact, scales = "free", ncol = 1, 
             axes = "all", strip.position = "top", 
             axis.labels = "all_x", 
             labeller = labeller(impact =  label_parsed)) + 
  theme_bw() + 
  scale_shape_manual(values = c("circle", "square")) +
    scale_color_manual(values = custom_colors) +
 theme(legend.position = "none",
        axis.text = element_text(size = 8), 
        axis.title = element_text(size = 10), 
        legend.text = element_text(size = 10), 
       strip.placement = "outside", 
       strip.background = element_blank(), 
        strip.text = element_text(size = 10))+
  xlab("Impact per kg product") + 
  ylab("Direct Regulations")+ 
  scale_x_continuous(labels = scientific) + 
  scale_y_continuous(labels = comma) + 
  labs(color = "Food Sector", shape = "Source")

figs3b <- footprint2 %>%
    ggplot() + 
  geom_point(aes(x = median, y = env_regulations, shape = author, color = sector), alpha = 0.2, size =3) +
  geom_errorbarh(aes(xmin=lower, xmax=upper, y = env_regulations, color = sector, height = 2000), alpha = 0.2)  +
  facet_wrap(~impact, scales = "free", ncol = 1, 
             axes = "all", strip.position = "top", 
             axis.labels = "all_x", 
             labeller = labeller(impact =  label_parsed)) + 
  theme_bw() + 
  scale_shape_manual(values = c("circle", "square")) +
    scale_color_manual(values = custom_colors) +
 theme(legend.position = "none",
        axis.text = element_text(size = 8), 
        axis.title = element_text(size = 10), 
        legend.title = element_text(size = 10), 
       strip.placement = "outside", 
       strip.background = element_blank(), 
       strip.text = element_text(size = 10))+
  xlab("Impact per kg product") + 
  ylab("Direct Environmental Regulations")+ 
  scale_x_continuous(labels = scientific) + 
  scale_y_continuous(labels = comma) + 
  labs(color = "Food Sector", shape = "Source")


figs3 <- ggarrange(figs3a, figs3b, 
                   common.legend = TRUE, 
                   legend = "bottom", 
                   labels = c("A", "B"))

ggsave("FigS3_final.png", figs3,width = 10, height = 12, dpi = 300)
```

#Figure S4: Sensitivity analysis for P&N data
```{r}
figs4 <- read_xlsx("Supplementary_Dataset_1.xlsx", "Figure S4",  trim_ws = F)

s4 <- figs4 %>%
    ggplot() + 
  geom_point(aes(x = production_emissions, y = total_regulations, color = sector), alpha = 0.2, size =3) +
  theme_bw() + 
    scale_color_manual(values = c("#0D98BA","#EC9706","#A52A2A" )) +
 theme(legend.position = "none",
        axis.text = element_text(size = 8), 
        axis.title = element_text(size = 10), 
        legend.text = element_text(size = 10), 
       strip.placement = "outside", 
       strip.background = element_blank(), 
        strip.text = element_text(size = 10))+
  xlab("Production emissions (kg CO2 per kg product)") + 
  ylab("Direct Regulations")+ 
  scale_y_continuous(labels = comma) + 
  labs(color = "Food Sector", shape = "Source")

ggsave("FigS4_final.png", s4, width = 5, height = 4, dpi = 300) 
```
